Response to Reviewer One

### 2021-05-06 Scripts/Reviews/reviewer_one.Rmd
Addressed all but one comment from Rev. 1

- Response:

@@

- **Response:** We are very limited in terms of word counting in the abstract so unfortunately, we cannot include specifics here. However, we have included some in-text examples, please see line *XXX* of page *XX*.

@@

- *Response:* Similarly, we have included some discussion of regarding adapted management programs, please see line *XXX* of page *XX*.

@@

- *Response:* We have changed this sentence to *Marine species’ distributions mainly reflect species’ preferences for discrete environmental conditions (2).*

@@

- Response:

@@

- Response:

@@

- **Response:** Thank you for your comment. We provide direction of change in the next figure (Figure 5 of the revised manuscript) showing winners and losers according to neighboring EEZs. Here we show how each neighboring EEZ will stand to win or lose against its neighbors. **NOTE FOR CO-AUTHORS:** *I am hesitant of actually pointing out winners and losers (e.g., stating that Spain will loos most of its catch to France). Hence, I rather leave the results and discussion more general. THoughts?*

@@

- *Response:* Thank you for this comment. We have included a couple of examples of management plans that are somehow prepared or have respond to the issues we highlight.

@@

- **Response:** Thank you for your comment. For this paper we used one climate model (the GFDL) forced following one climate change scenario (RCP 8.5) to couple with one species distribution model. For this reason, providing quantitative upper and lower bounds of our results is not possible and would require substantial extra computation. However, because we have 10 different runs of the GFDL we are capable of providing a a less conservative estimate of the numbers you mention (i.e., the number of shifting stocks and EEZs). This was originally presented in the methods section as a sensitivity analyses and has now been moved to the Methods section of the main paper. It reads on line *XXX* of page *XX*: *We also computed a less conservative estimation of shifting transboundary stocks by including a threshold of one standard deviation (i.e., representing a probability of 68% that the stock had shifted from natural variation; see methods). In this case, the global average shift in the shared distribution of transboundary stocks is 2029 $\pm$ 27 years, a difference of about 7 years (Fig. S8). In total, 5,745 transboundary stocks would shift their shared distributions between 2006 and 2100 considering a less conservative metric, that is, 33% (n = 1626) more shifting stocks (Figs. S2 and S8).*

>>>>

- Response: Thank you very much for commenting on our figures. Here, we provide responses to the two large scale questions you provide and below we respond the finer scale points. We hope that this clarifies all of your comments.

 - **Regarding the bi-lateral agreements**, this is a great question that, unfortunately, we cannot respond at this moment. Currently, there is only one database on bi-lateral agreements produce by Oremus *et al* (2020). On their paper, the authors state "we analysed 27 publicly available international fisheries agreements in the South Pacific, Southeast Asia, South Asia, Northwest Africa, and Central America and the Caribbean" and " For each agreement, we recorded the following information... If relevant, to which specific stock or species the agreement pertained". However, the authors do not provide any information at the stock level and, unfortunately, they never respond/ did not shared their database with us.

We hope that the reviewer understands the complexity of building such database and that this exercise falls outside the scope and stage of our current analysis. We agree that having such information would increase the manuscript impact, but, would not necessarily directly impact our results nor the message we want to covein (Ultimately oremus *et at* state it very clearly in their paper, "None of the 127 agreements contains language that is directly related to climate change, range shifts or stock exits").

Oremus KL, Bone J, Costello C, Molinos JG, Lee A, Mangin T, Salzman J. 2020. Governance challenges for tropical nations losing fish species due to climate change. Nature Sustainability 6:1–4. Nature Publishing Group. Available from https://www.nature.com/articles/s41893-020-0476-y.

 - **Regarding model-specific variance.** For this paper we used one climate model (the GFDL) forced following one climate change scenario (RCP 8.5) to couple with one species distribution model. For this reason, providing quantitative upper and lower bounds of our results is not possible and would require substantial extra computation. However, because we have 10 different runs of the GFDL and employ the time of emergence concept, we are capable of providing a less conservative estimate of the numbers you mention (i.e., the number of shifting stocks and EEZs). This was originally presented in the methods section as a sensitivity analysis and has now been moved to the Methods section of the main paper (**NOTE TO CO-AUTHORS**: Should we include this in the results?). It reads on line *XXX* of page *XX*: *We also computed a less conservative estimation of shifting transboundary stocks by including a threshold of one standard deviation (i.e., representing a probability of 68% that the stock had shifted from natural variation; see methods). In this case, the global average shift in the shared distribution of transboundary stocks is 2029 $\pm$ 27 years, a difference of about 7 years (Fig. S8). In total, 5,745 transboundary stocks would shift their shared distributions between 2006 and 2100 considering a less conservative metric, that is, 33% (n = 1626) more shifting stocks (Figs. S2 and S8).*

@@

- **Response:** We are very limited in terms of word counting in the abstract so unfortunately, we cannot include specifics here. Please note that we do provide some in-text examples in the results section, specifically the revised Figure 4.

@@

- **Response:** Similarly, we do not have space to discuss this here. Please note that we discuss management plans on the paragraph starting on line *13* of page *12*.

@@

- **Response:** We have changed this sentence to *Marine species’ distributions mainly reflect species’ preferences for discrete environmental conditions (2).*

@@

- **Response:** Please see the main comment response above.

@@

- *Response:* In the section "High present-day climate risk of on transboundary fisheries management" we describe early shifts in the shared distribution of transboundary stocks including the cases of Humboldt squid (*Dosidicus gigas*) and Atlantic mackerel (*Scomber scombrus*) both in the early 2000s. We have included some more punctual examples of documented shifts between 2006 and 2021. It reads on line **xx** of page **XX**: "Similar shifts have been documented for multiple European stocks [@Baudron:2020dj] like European hake (*Merluccius merluccius*) [@Baudron:2015il] as well as...

@@

- **Response:** Thank you for your comment. We provide direction of change in the next figure (Figure 5 of the revised manuscript) showing winners and losers according to neighboring EEZs. Here we show how each neighboring EEZ will stand to win or lose against its neighbors. **NOTE FOR CO-AUTHORS:** *I am hesitant of actually pointing out winners and losers (e.g., stating that Spain will loos most of its catch to France). Hence, I rather leave the results and discussion more general. Thoughts?*

@@

- **Response:** Thank you for this comment. We have eddited the paragraph starting at line **13** of page **12** to reflect this comment.

@@

- **Response:**  Please see the response to the main comment above.
